Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey

### 2017-08-22 cloverflow_technical_report/cloverflow_survey_rn.tex
Small fix.

In addition, we found that almost all of the answerers in both groups (98\% and
99\% respectively) do not include license statement in their code snippets
(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
gave more information regarding this question in the open comment question and
we summarised them into three groups as follows. First, some answerers chose to post only their
own code or code that was adapted from the question. They are hence
automatically subjected to CC BY-SA 3.0. Second, they copied code from company
or open source projects that they knew were permitted to be publicly
distributed. Third, some answerers believe that code snippets in their answers
are too small to claim any intellectual property on them and fall under fair
use~\citep{fairuse}.

>>>>

In addition, we found that almost every answerer in both groups (98\% and
99\% respectively) do not include license statement in their code snippets
(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
gave more information regarding this question in the open comment question and
we summarised them into three groups as follows. First, some answerers chose to post only their
own code or code that was adapted from the question. They are hence
automatically subjected to CC BY-SA 3.0. Second, they copied code from company
or open source projects that they knew were permitted to be publicly
distributed. Third, some answerers believe that code snippets in their answers
are too small to claim any intellectual property on them and fall under fair
use~\citep{fairuse}.
